### 2017-04-10 thesis/latex/thesis.tex
Make build.

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../plots/kb-kub-contour}
  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state. Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.}
  \label{fig:kb-kub-heatmap}
\end{figure}

@@

\section{Chapter: Discussion}
\subsubsection{Limitations}
Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information, other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be springy...

@@

Computational limitations: Our project is computational, not experimental. Thus the onus is on us to show that our system is not a humongously over-fit model which just happens to reproduce experimental data, but rather a good physical model of dynein which also replicates data.\\

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../figures/kb-kub-contour}
  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state. Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.}
  \label{fig:kb-kub-heatmap}
\end{figure}

@@

\section{Chapter: Discussion}
\subsubsection{Limitations}
The accuracy of correspondence between model dynein and physical dynein is very relevant when assessing the meaningfulness of the simulation results. Reducing a megaDalton weight protein to a five-coordinate kinematic model with springy hinges is bound to have low resolution. However, the point of this model is to predict gross stepping behavior over large timescales. Thus, only assumptions which possibly add large systematic errors to stepping behavior are of interest. These possible limitations are listed below.\\

\paragraph{Spherical domains}
Domain shape influences primarily the drag coefficients $\gamma$ of the model. These in turn affect the diffusion rate of different domains. Reducing domains to spheres adds a systematic error to the diffusion speed of each domain, which could bias step size. However, spring constants $c_b$, $c_m$ and $c_t$ also have an influence on the diffusion rate of spheres. Thus by fitting spring constants to the proper step length, the systematic error of domain size can be reduced -- ???\\

-------------------------------------
Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information, other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be springy...

@@

Computational limitations: Our project is computational, not experimental. Thus the onus is on us to show that our system is not a humongously over-fit model which just happens to reproduce experimental data, but rather a good physical model of dynein which also replicates data.\\
-------------------------------------
